Tree size, microhabitat, and hydraulic traits (interactively) shape drought response in a temperate broadleaf forest

### 2019-08-03 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
added hypotheses/predictions summary table
relates to issue #46

@@

  * P1.3- There is a negative interactive effect between tree height and topographic water index. ([issue #45](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/45))

@@

2.3. Size-dependent drought resistance is driven by--or alternatively, buffered by--functional traits (i.e., larger trees have more drought vulnerable traits).
    * P2.3 Inclusion of traits in the statistical model does not eliminate or significantly reduce effect of tree size (or TWI). That is, the effects of height and and microhabitat will not be negated in the best model including size, microhabitat, and traits.  (supported)

**3. Did responses vary across droughts?**
3.1 Overall community response is proportional to the severity of each drought.

    * P3.1 -  (How do you define severity? min PDSI? duration? it may be tricky to find the right metric, but I agree that its interesting to compare across droughts)

@@

**Table 1. Species analyzed here, listed in descending order of ANPP_stem. n cores and DBH range represented, and species traits** [*This replaces/combines the two remaining tables in this section. Suggested columns, with those to include only if they fit in parentheses: species, (stems >=10 cm per ha in plot), (ANPP_stem), n cores, DBH range of cores, (n cores in each crown position) species means for each trait]

>>>>

**Table 1. Summary of hypotheses, predictions and results** We count predictions as fully supported (or rejected) when the direction of response matches (or contradicts) the prediction and model dAIC≥2 relative to the approriate null model or to any alternative multivariate model with within 2 dAIC. Parentheses indicate that predictions were partially supported (or rejected)-- i.e., with direction of response matching (or contradicting) the prediction but model dAIC<2 relative to the approriate null model, when response partially matched predicted order for categorical variable (canopy position), or when an alternative multivariate model within 2 dAIC had a contradictory response.  (Table 1.xlsx)

(The content below needs to be re-written / mostly removed to go with Table 1.)

@@

  * P1.3- There is a negative interactive effect between tree height and topographic water index. (rejected- [issue #45](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/45))

@@

2.3. Size-dependent drought resistance is driven by--or alternatively, buffered by--functional traits (i.e., larger trees have more drought vulnerable traits).

  * P2.3 Inclusion of traits in the statistical model does not eliminate or significantly reduce effect of tree size (or TWI). That is, the effects of height and and microhabitat will not be negated in the best model including size, microhabitat, and traits.  (supported)

**3. Did responses vary across droughts?**
3.1 Overall community response is proportional to the severity of each drought.  (Do you really want to add this hypothesis? How do you define severity? min PDSI? duration? it may be tricky to find the right metric, but I agree that its interesting to compare across droughts)

@@

**Table 2. Species analyzed here, listed in descending order of ANPP_stem. n cores and DBH range represented, and species traits** [*This replaces/combines the two remaining tables in this section. Suggested columns, with those to include only if they fit in parentheses: species, (stems >=10 cm per ha in plot), (ANPP_stem), n cores, DBH range of cores, (n cores in each crown position) species means for each trait]
